The Effectiveness of Strategies to Contain SARS-CoV-2: Testing, Vaccinations, and NPIs

### 2022-03-08 src/paper/results/robustness_to_sensitivity_assumptions.tex
Talk about pre and asymptomatics' Ct values.

% what is available -> two step mapping
Unfortunately, such sensitivity profiles are not usually reported in studies. We
thus need to create them by combining two types of studies: 1. Studies that
report the viral load in terms of threshold cycle ($C_t$) values determined by
PCR test (e.g. \cite{Cosentino2022}, \cite{Ong2021}, \cite{Bonnet2022},
\cite{Jang2021} and \cite{Zuin2021}). 2. Studies that report the ensitivity of
rapid tests for different $C_t$ values (e.g. \cite{Scheiblauer2021},
\cite{Bruemmer2021}).

% what options do we have to configure the mappings
It is natural to assume that the evolution of $C_t$ values over time as well as
the effect of $C_t$ values on rapid test sensitivity are continuous functions.
However, the results of the available studies are usually reported in a
discretized way. This leads to multiple ways of calculating the sensitivity
profiles. Some try to recover the underlying continuous functions using
interpolation or regression, others simply use the discretized values.

% Describe CT value formula vs. bin averages
For the calibration of $C_t$ values over time we can either use discretized
values for several time bins from \cite{Ong2021} and \cite{Jang2021}.
Alternatively, we can use linearized formulas for calculating sensitivities over
time \cite{Cosentino2022}.

% Describe sensitivity lookupd vs. interpolation
For the mapping of $C_t$ values to rapid test sensitivities, again we have two
options. First, we can simply look up the discretized values for the three $C_t$
provided in \cite{Scheiblauer2021} (below 20, 25 to 30 and above 35). Secondly,
we can use linear regression to estimate a continous mapping for the
relationship by assuming that the $C_t$ values of each bin are achieved exactly
at the bin midpoints and that the relationship is linear.

>>>>

% what is available -> two step mapping
Unfortunately, such sensitivity profiles are not usually reported in studies. We
thus need to create them by combining two types of studies: 1. Studies that
report the viral load in terms of threshold cycle ($Ct$) values determined by
PCR test (e.g. \cite{Cosentino2022}, \cite{Ong2021}, \cite{Bonnet2022},
\cite{Jang2021} and \cite{Zuin2021}). 2. Studies that report the ensitivity of
rapid tests for different $Ct$ values (e.g. \cite{Scheiblauer2021},
\cite{Bruemmer2021}).

% what options do we have to configure the mappings
It is natural to assume that the evolution of $Ct$ values over time as well as
the effect of $Ct$ values on rapid test sensitivity are continuous functions.
However, the results of the available studies are usually reported in a
discretized way. This leads to multiple ways of calculating the sensitivity
profiles. Some try to recover the underlying continuous functions using
interpolation or regression, others simply use the discretized values.

% Describe CT value formula vs. bin averages
For the calibration of $Ct$ values over time we can either use discretized
values for several time bins from \cite{Ong2021} and \cite{Jang2021}.
Alternatively, we can use linearized formulas for calculating sensitivities over
time \cite{Cosentino2022} and complement it with interpolations of data points
from \cite{Jang2021} in the pre-infectious stage. Throughout we assume that the
$Ct$ values of individuals who eventually develop symptoms and those who do not
follow the same trajectory. This is in line with results by \cite{Zuin2021} and
recent evidence that rapid tests excel at discovering asymptomatic cases
\cite{Rosella2022}.

% Describe sensitivity lookupd vs. interpolation
For the mapping of $Ct$ values to rapid test sensitivities, again we have two
options. First, we can simply look up the discretized values for the three $Ct$
provided in \cite{Scheiblauer2021} (below 20, 25 to 30 and above 35). Secondly,
we can use linear regression to estimate a continous mapping for the
relationship by assuming that the $Ct$ values of each bin are achieved exactly
at the bin midpoints and that the relationship is linear.
